Reviewer comments from PeerJ

### 2015-02-19 PeerJResponse.tex
Edit to response letter
Edits to response

4) It would be helpful to include Fig. S1 in the main text of the paper and to label the two sequenced regions (Region 1 and 2) in the figure itself (not just in the caption). \\
\lev{Okay can do this}
\mbh{yep, easy to do and this is an online publication without figure charges so why not!}

>>>>

4) It would be helpful to include Fig. S1 in the main text of the paper and to label the two sequenced regions (Region 1 and 2) in the figure itself (not just in the caption). \\

\res{Thank you for the suggestion. We have included Fig. S1 in the main manuscript, now labelled Fig. 1, and have added labels for the two sequenced regions, Region 1 and Region 2.}

\lev{Hi guys, I'm having trouble getting the figures to renumber in order and haven't been able to figure out what's going on, if either of you knows how to fix or has a suggestion.}
